Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-05 paper_jasa.tex
caption for figure 13 updated

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.55}{\includegraphics{p_val_definition.pdf}}
       \caption{Conventional test $p$-value ($p_D$) vs visual $p$-value obtained from the definition . Values are shown on square root scale. For experiment 3, $p$-values of uncontaminated part of the data are also shown.}
    %   \hh{Mahbub, another change: could you change the y label to 'estimate of visual p-value $\hat{p_D}$ ?}
       \label{fig:pval_definition}
\end{figure*}

@@

\begin{figure}[hbtp]
   \centering
%       \scalebox{0.60}{\includegraphics{choice_reason.pdf}}
%       \scalebox{0.60}{\includegraphics{choice_reason_count.pdf}}
       \includegraphics[width=0.45\textwidth]{choice_reason2.pdf}
       \includegraphics[width=0.45\textwidth]{choice_reason3.pdf}
       \caption{Reasons for choosing the plot in a lineup for experiment 3. Reason 12 means both reasons 1 and 2 are chosen. Number of subjects choosing that reason are shown on the right hand side. Notice that 345 people choose only reason (3) "Clustering visible", out of whom 64\% got the actual plot (proportion correct = 0.64), which indicates there are number of people who choose the right plot for wrong reason (Type-III error). Those who chose reason 123 got the actual plot about 97\% times.}
       \label{fig:choice_reason}
\end{figure}

>>>>

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_definition.pdf}}
       \caption{Conventional test $p$-value ($p_D$) vs visual $p$-value obtained from the definition . Values are shown on square root scale. For experiment 3, $p$-values of uncontaminated part of the data are also shown.}
    %   \hh{Mahbub, another change: could you change the y label to 'estimate of visual p-value $\hat{p_D}$ ?}
       \label{fig:pval_definition}
\end{figure*}

@@

\begin{figure}[hbtp]
   \centering
%       \scalebox{0.60}{\includegraphics{choice_reason.pdf}}
%       \scalebox{0.60}{\includegraphics{choice_reason_count.pdf}}
       \includegraphics[width=0.45\textwidth]{choice_reason2.pdf}
       \includegraphics[width=0.45\textwidth]{choice_reason3.pdf}
       \caption{Exploring the reasons for plot choices for experiment 3, to examine the occurrence of Type III error. The vertical axis shows the reasons. At left, all subjects choices are shown, and reason 123 means all three reasons are used. At right, if the subject used a reason, regardless if they also used more than this reason, they are counted. The horizontal axis shows the proportion of times the subjects correctly chose the actual data plot. Size of the point corresponds to the number of subjects using that reason.}
       \label{fig:choice_reason}
\end{figure}
